Pricing Used Sailboats : A Combination Model Based on Heuristic Multilevel Regression and Deep Forest

### 2023-04-03 Paper/PAPER.tex
paper

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2332102]{easymcm}  % 载入 EasyMCM 模板文件
\problem{Y}  % 请在此处填写题号
%\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
\usepackage{newtxtext}
\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}} 
\title{Title}  % 标题

@@

    For Problem(a), We adopt a \textbf{Heuristic Multilevel Regression Model} inspired by the conclusion drawn from data analysis, and introduce the concept of \textbf{impurity} to heuristically evaluate interrelation among variables, avoid bias by introducing \textbf{feedback and renormalization}.
    And our model achieves good precision on both the train set and the test set.

@@

	Symbol& Definition\\
	\midrule
	$l$ &Measurement data\\
    \hline
	$L$ &Feature vector\\
    \hline
	$F$ &The dimension of $L$\\
    \hline
    $k$ &Search range\\
    \hline
    $\lambda$ & The feature values of natural neighbors\\
    \hline
    $nb_k(l)$ & The number of reverse neighbors of $l$ in the $k$-th iteration\\
    \hline
    $R$ & Correlation coefficient\\
    \hline
    $\hat{y}$ & The estimated value of $y$\\
    \hline
    $\hat{\beta}$ & The estimated value of the regression coefficients\\
    \hline
    $X, Y$ & The variables for which the correlation is to be tested \\
    \hline
    $P$ & Measured value \\
    \hline
    $Q$ & Simulated value \\ 
	\bottomrule
\end{tabular}
\end{center}
\end{table}
\section{Data Exploration}

@@

\subsection{The Establishment of The Model}
\subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}

\emph{Model 1}, as illustrated in Figure \ref{fig:Model1}, is specifically designed to predict prices by taking into account input variables such as Year, Region, and Variant. To achieve accurate predictions, this model incorporates a heuristic hierarchical multiple regression approach, which distinguishes it from conventional regression methods. This innovative technique allows for a more nuanced understanding of the relationships between variables, ultimately leading to improved performance and reliability.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=.8\textwidth]{accuracy.jpg}
        \caption{Model Fitting Accuracy}\label{fig:accuracy}
\end{figure}

@@

\section{Regional Effect Analysis}
Applying \emph{Model 1}, we can easily abstract the effect of each region. 
Therefore, by normalizing the year and variant, 
we can clearly see the effect of each region(see Figure \ref{fig:region_effect}).

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{region_effect.png}
    \caption{Region's Effect}\label{fig:region_effect}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width=.8\textwidth]{accuracy.jpg}
    \caption{Model Fitting Accuracy in HongKong}\label{fig:HongKong}
\end{figure}

@@

@@

@@

Figure 3 reveals a strong linear correlation between price and year. The model shows that the Region's Effect influences market prices by affecting boat types. In particular, areas with higher per capita GDP tend to buy more expensive boat types, leading to higher average prices for used boats in these regions.

\noindent \textbf{\emph{Part Three - Model of Hong Kong}}

@@

>>>>

% 本模板不需要填写年份，以当前电脑时间自动生成
% 请在以下的方括号中填写队伍控制号
\usepackage[2332102]{easymcm}  % 载入 EasyMCM 模板文件
\problem{Y}  % 请在此处填写题号
%\usepackage{mathptmx}  % 这是 Times 字体，中规中矩 
%\usepackage{mathpazo}  % 这是 COMAP 官方杂志采用的更好看的 Palatino 字体，可替代以上的 mathptmx 宏包
\usepackage{newtxtext}
\newcommand{\upcite}[1]{\textsuperscript{\textsuperscript{\cite{#1}}}} 
\title{Pricing Used Sailboats : A Combination Model Based on Heuristic Multilevel Regression and Deep Forest}  % 标题

@@

    For Problem(a), Inspired by the previous conclusion, we adopt a \textbf{Heuristic Multilevel Regression Model} for making the three \emph{discrete} variables \emph{continuous}, introduce the concept of \textbf{impurity} to heuristically evaluate interrelation among variables, and avoid bias by introducing \textbf{feedback and renormalization}. Finally, we use \textbf{Deep Forest} to regress them to the price.
    And our model achieves good precision on both the train set and the test set.

@@

	Symbol& Definition\\
	\midrule
	$l$ &Measurement data\\
    \hline
	$L$ &Feature vector\\
    \hline
	$F$ &The dimension of $L$\\
    \hline
    $k$ &Search range\\
    \hline
    $\lambda$ & The feature values of natural neighbors\\
    \hline
    $nb_k(l)$ & The number of reverse neighbors of $l$ in the $k$-th iteration\\
    \hline
    $R$ & Correlation coefficient\\
    \hline
    $\hat{y}$ & The estimated value of $y$\\
    \hline
    $\hat{\beta}$ & The estimated value of the regression coefficients\\
    \hline
    $P$ & Measured value \\
    \hline
    $Q$ & Simulated value \\ 
    \hline
    $\alpha$ & p-value significance level \\
    \hline
    $df$ & freedom \\
    \hline
    $s$ & standard deviation \\
    \hline 
    $T$ & t-distribution \\

	\bottomrule
\end{tabular}
\end{center}
\end{table}

\section{Data Exploration}

@@

\subsection{The Establishment of The Model}
\subsubsection{Model 1 \textemdash  Heuristic Hierarchical Multiple Regression}
Inspired by the conclusion drawn from data analysis, we adopt a multilevel heuristic model that utilizes the purity of the samples grouped by specific variables.  We introduce impurity to model a variable's independence from other variables.

To be specific, we begin with the year variable mentioned above.

The impurity by a variable can be measured by the weighted mean variance of all groups divided by the variable.

Unavoidably, the initial impurity will damage our model's accuracy. For example, we have supposed that the year variable is independent of other variables for the first round of normalization (otherwise we cannot resolve the problem at the beginning), making our normalizing coefficient of this variable biased.

Therefore, we introduce the feedback model into our model. To be exact,   after the first round has been completed, compared to the initial state, we have more information about the year, variant, and region factors' effect. Therefore, we repeatedly renormalize the factors to gain a more accurate coefficient (factors' effect).

Specifically, \emph{Model 1}, as illustrated in Figure \ref{fig:Model1}, is specifically designed to predict prices by taking into account input variables such as Year, Region, and Variant. To achieve accurate predictions, this model incorporates a heuristic hierarchical multiple regression approach, which distinguishes it from conventional regression methods. This innovative technique allows for a more nuanced understanding of the relationships between variables, ultimately leading to improved performance and reliability.

@@

    \begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{.4\textwidth}
        \includegraphics[width=\textwidth]{accuracy1.jpg}
        \caption{The fitting performance before denoising.}\label{subfig:accuracy1}
        \end{subfigure}
        \begin{subfigure}[b]{.4\textwidth}
        \includegraphics[width=\textwidth]{accuracy2.png}
        \caption{The fitting performance after denoising.}\label{subfig:accuracy2}
        \end{subfigure}
        \caption{Model Fitting Accuracy in HongKong}\label{fig:accuracy}
    \end{figure}

@@

\section{Regional Effect Analysis}

Applying \emph{Model 1}, we can easily abstract the effect of each region. 
Therefore, by normalizing the year and variant, 
we can clearly see the effect of each region(see Figure \ref{fig:region_effect1}).

\begin{figure}[htbp]
    \centering
    \includegraphics[width=1\textwidth]{region_effect1.png}
    \caption{Region's Effect}\label{fig:region_effect1}
\end{figure}

After normalizing the year and the variant factor (thus eliminating their influence), we surprisingly find that the distribution of average price among regions turns much more uniform than that of the initial state. Moreover, the imparity by variants is small as soon as the year factor is normalized(see Figure \ref{fig:region_effect2}). So we can conclude that the regional effect is not significant across variants. And it's necessary to note that the regional effect mainly takes effect by featuring variants of different prices.

Practically, the economic development level of the region best describes the region effect we found. Statistically, the GDP per capita is found of a strong positive linear correlation with the average variant prices of a region with linear correlation coefficient and p-testing.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.9\textwidth]{region_effect2.png}
    \caption{Region's Effect after nomarlizing Variant}\label{fig:region_effect2}
\end{figure}

To verify the significance of linear correlation, we should perform p-testing:
Assuming that we choose $\alpha$ as the significance level for the p-value test (usually 0.01, 0.05, or 0.10) and the hypothesis is denoted as $H_0$, we first calculate the means and standard deviations of the two samples, denoted as $\bar{x}$ and $s$. Then, we calculate the t-value using the following formula:
$$t=\frac{\bar{x}_1-\bar{x}_2}{\sqrt{\frac{s_1^2}{n_1}+\frac{s_2^2}{n_2}}}$$

We calculate the degrees of freedom as $df = n_1 + n_2 - 2$, and then use the degrees of freedom and the significance level to look up the critical value of t from the t-distribution table with n-1 degrees of freedom. From this, we obtain the p-value:
$$p=2\times P(T>|t|)$$

Because we need to make a judgment about the correctness of the hypothesis $H_0$, we need to perform the following evaluation:
$$\begin{cases}
    p \geq\alpha ,\quad cannot \quad reject\quad H_0\\p<\alpha,\quad can \quad reject\quad H_0
    \end{cases}$$

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{HK1.png}
    \caption{Monohulled Sailboats}\label{subfig:HK1}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{HK2.png}
    \caption{Catamaran}\label{subfig:HK2}
    \end{subfigure}
    \caption{Model Fitting Accuracy in HongKong}\label{fig:HK}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{strength1.png}
    \caption{Single Cycle}\label{subfig:SG1}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{strength2.png}
    \caption{Muticycle}\label{subfig:SG2}
    \end{subfigure}
    \caption{Model accuracy improvement}\label{fig:strength}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{report1.png}
    \caption{Monohulled Sailboats}\label{subfig:report1}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{report2.png}
    \caption{Catamaran}\label{subfig:report2}
    \end{subfigure}
    \caption{Model Fitting Accuracy}\label{fig:Report1}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{monohulled_price_year.png}
    \caption{Monohulled Sailboats}\label{subfig:report3}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{catamaran_price_year.png}
    \caption{Catamaran}\label{subfig:report4}
    \end{subfigure}
    \caption{The relationship between year and price}\label{fig:Report2}
\end{figure}

Figure 15 reveals a strong linear correlation between price and year. The model shows that the Region's Effect influences market prices by affecting boat types. In particular, areas with higher per capita GDP tend to buy more expensive boat types, leading to higher average prices for used boats in these regions.
\clearpage
\noindent \textbf{\emph{Part Three - Model of Hong Kong}}

\begin{figure}[htbp]
    \centering
    \includegraphics[width=.5\textwidth]{report5.jpg}
    \caption{Optimizing Model Performance}\label{fig:Report3}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[b]{.45\textwidth}
    \includegraphics[width=\textwidth]{report3.png}
    \caption{Monohulled Sailboats}\label{subfig:report5}
    \end{subfigure}
    \begin{subfigure}[b]{.4\textwidth}
    \includegraphics[width=\textwidth]{report4.png}
    \caption{Catamaran}\label{subfig:report6}
    \end{subfigure}
    \caption{Preferences for boat lengths vary among different regions}\label{fig:Report4}
\end{figure}
